Bricking up backdoors in Intrusion Detection Systems

### 2019-09-13 paper/paper.tex
Minor correction

We used go-flows~\cite{vormayr_cn-tu/go-flows_2019}
% flow exporter
for extracting features from the raw capture files and applied Z-score normalization to process the data. We used 3-fold cross validation to ensure that our results do not deviate significantly across folds.

@@

%\includegraphics[width=\columnwidth]{figures/pdpale2017nn_zoom.pdf}
\caption{\gls{pdp} and \gls{ale} plots of the \gls{mlp} for the \cic{}. Full range of TTL values on top; only TTL values from 0 to 5 below.}
\label{fig:pdp_ttl}
\end{figure}

>>>>

We used go-flows~\cite{vormayr_go-flows_2019}
% flow exporter
for extracting features from the raw capture files and applied Z-score normalization to process the data. We used 3-fold cross validation to ensure that our results do not deviate significantly across folds.

@@

%\includegraphics[width=\columnwidth]{figures/pdpale2017nn_zoom.pdf}
\caption{\gls{pdp} and \gls{ale} plots of the \gls{mlp} for \cic{}. Full range of stdev(TTL) values on top; stdev(TTL) values from 0 to 5 below.}
\label{fig:pdp_ttl}
\end{figure}
